---
title: "Introduction"
author: "Kevin Li"
date: "2024-02-07"
output: html_document
---

## 1. Load `lidR` package

We are using the `lidR` package to process liDAR data from Puerto Rico.

```{r load_lidr}


```

## 2. Load LAS files

The liDAR data consists of point clouds stored in .las (LAS) files. These can be loaded into `R` using the `lidR` function `readLAS()`. Use `readLAS()` to load in one of the `LAS` files from the data folder.

```{r readLAS}



```

## 3. Plot LAS files

The loaded LAS file can be viewed simply using the `plot()` function. This brings up a 3D viewer that lets you pan and zoom around the LAS point cloud. Try plotting the point cloud you loaded. The argument `color` lets you determine which attribute to use to color points. By default, the Z axis is used for color. Find what other attributes are available for plotting and change the attribute used for coloring the plot.

```{r plot_LAS}



```

## Ground classification

A key problem we are trying to solve is classifying the ground within the LAS point cloud. From looking at the point cloud plot, you can probably see where the ground is. We will be employing the function `classify_ground()` in `lidR` to use an algorithm to identify the ground. Try doing this for the LAS file you loaded, using the `pmf` algorithm. Follow the comments in the code chunk for visualizing the classified point cloud.

```{r classify_ground}

las_gnd <- classify_ground()


# Try plotting the classified points by their classification attribute to view results



# Another way of viewing the results is to plot a cross section.
# I've prepared a function in `functions/cross_section.r` to do this. Try this out.
# See the comments in that script for more details

source("functions/function_plotcross.r")

```

## Bulk data handling

We have many LAS files to process, so it is advantageous to do some automation. Use the `list.files()` function to read in the names of all the .las files in the data folder and store them in the vector `las.names`. Load these file names into the `R` session using a loop and store them in a list object (`las.list`)

```{r bulk_data}

# create a vector to hold the las file names to be loaded called `las.names`
las.names <- 

# load the .las files in `las.names` using a loop
# Write the loaded files to the list object `las.list`, created below:
las.list <- list()

```

With all the las files loaded, we can process them in bulk. Use any method you like to perform ground classification on all the las files loaded in `las.list`.

```{r bulk_classification}


```

Use the `plot_cross_class` function you tried out above to plot cross sections for each LAS file. Save the plot of each LAS file as a .png with a systematic name. You could use the function `ggsave()` for this.

```{r bulk_output}


```
